Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2014-01-10 paper.tex
Use 'we' everywhere.
Sometimes 'we' was followed a few words down by 'my', other times 'I' was used right after a sentence using 'we'.

Today, if we want to load a page from \emph{www.facebook.com}, my computer will have to first get the Domain Name System record matching that domain. DNS was designed in a hierarchical way and TLD registrations are handled by a single organisation, the ICANN.

@@

But how can we verify authenticity? 
Even if my Domain Name System returns the right IP address, how do I know for sure that I'm establishing a connection with the client I want ? Today, we are using yet another hierarchical system to verify authenticity, namely \emph{SSL certificates}. This means that in addition to trusting ICANN, we will have to trust hundreds of Root Certificate Authorities that are shipped with our browsers.\cite{mozillaSSL}

@@

If I want to add some blocks (list of transactions) to the blockchain, I will have to solve this problem
\begin{center}
SHA-256("TransactionsInfo" + challengeNumber) =< target
\end{center}
where \emph{transactionsInfo} is a parameter list of information about the transactions in the blocks (and some extra information like a return address for the reward). The blockchain is vulnerable to some malleability regarding certain informations in the transaction but all the important information (such as the amount of the transaction, the recipient and the sender) is part of this hash.
The challenge the miner has to solve --- the proof-of-work --- is to find the number such that when we append the transactions' infos to this number, and hash the combination, the output hash is smaller than a given number.
We notice that this certain challenge number is established by the network and determines how hard the problem is. In Bitcoin, this number is dynamically adjusted to keep an approximate block validation time of 10 minutes.\cite{hashCash}

@@

Miners are rewarded for their efforts. First, when making a transaction, I can speed up the money transfer by adding a transaction fee, that will go directly to the miners. Mining software is thus optimised to sort the transactions, in order to be merged in blocks by decreasing order of transaction fee. 
The other reward from mining comes from the coinbase transaction : mining does generate money.  At the creation of Bitcoin, this reward was set to be a 50 BTC. But for every 210,000 validated blocks (once every four years) the reward halves. This has happened just once, to date, and so the current reward for mining a block is 25 bitcoins. This halving in the rate will continue every four years until the year 2140 CE. At that point, the reward for mining will drop below $10^{-8}$ bitcoins per block which is a satoshi, the smallest unit of Bitcoin and the total amount of bitcoins will cease to increase.

@@

This would make my website accessible at the \emph{fredericjacobs.bit}, a memorable, secure (a client can verify the fingerprint) and global address, the triangle has been squared!

>>>>

Today, if we want to load a page from \emph{www.facebook.com}, our computer will have to first get the Domain Name System record matching that domain. DNS was designed in a hierarchical way and TLD registrations are handled by a single organisation, the ICANN.

@@

But how can we verify authenticity? 
Even if our Domain Name System returns the right IP address, how do we know for sure that we are establishing a connection with the client we want ? Today, we are using yet another hierarchical system to verify authenticity, namely \emph{SSL certificates}. This means that in addition to trusting ICANN, we will have to trust hundreds of Root Certificate Authorities that are shipped with our browsers.\cite{mozillaSSL}

@@

If we want to add some blocks (list of transactions) to the blockchain, we will have to solve this problem
\begin{center}
SHA-256("TransactionsInfo" + challengeNumber) =< target
\end{center}
where \emph{transactionsInfo} is a parameter list of information about the transactions in the blocks (and some extra information like a return address for the reward). The blockchain is vulnerable to some malleability regarding certain informations in the transaction but all the important information (such as the amount of the transaction, the recipient and the sender) is part of this hash.
The challenge the miner has to solve --- the proof-of-work --- is to find the number such that when we append the transactions' infos to this number, and hash the combination, the output hash is smaller than a given number.
We notice that this certain challenge number is established by the network and determines how hard the problem is. In Bitcoin, this number is dynamically adjusted to keep an approximate block validation time of 10 minutes.\cite{hashCash}

@@

Miners are rewarded for their efforts. First, when making a transaction, we can speed up the money transfer by adding a transaction fee, that will go directly to the miners. Mining software is thus optimised to sort the transactions, in order to be merged in blocks by decreasing order of transaction fee. 
The other reward from mining comes from the coinbase transaction : mining does generate money.  At the creation of Bitcoin, this reward was set to be a 50 BTC. But for every 210,000 validated blocks (once every four years) the reward halves. This has happened just once, to date, and so the current reward for mining a block is 25 bitcoins. This halving in the rate will continue every four years until the year 2140 CE. At that point, the reward for mining will drop below $10^{-8}$ bitcoins per block which is a satoshi, the smallest unit of Bitcoin and the total amount of bitcoins will cease to increase.

@@

This would make our website accessible at the \emph{fredericjacobs.bit}, a memorable, secure (a client can verify the fingerprint) and global address, the triangle has been squared!
